Adaptive Approximation for Multivariate Linear Problems \\ with Inputs Lying in a Cone

### 2018-11-03 RICAM2018NovTalk.tex
Editing and expanding

\newcommand{\sol}{S}
\newcommand{\app}{A}
\newcommand{\Sapp}{S_{\textup{app}}}
\newcommand{\LambdaStd}{\Lambda^{\textup{std}}}
\newcommand{\LambdaSer}{\Lambda^{\textup{ser}}}
\newcommand{\LambdaAll}{\Lambda^{\textup{all}}}
\DeclareMathOperator{\spann}{span}
%\DeclareMathOperator{\app}{app}

@@

    \item \hyperlink{BallsWontHelp}{\beamergotobutton{But I really like balls!}}
\end{itemize}

@@

@@

\begin{align*}
    \cf &:= \left \{ f = \sum_{\vj \in \cn} \hf(\vj) u_{\vj} : \norm[\cf]{f} := \bignorm[1,\vlambda]{\hf} : = \norm[1]{\left(\frac{\bigabs{\hf(\vj)}}{\lambda_{\vj}} \right)_{\vj \in \cn}} \right \}\\
    u_{\vj} &= \text{Cosine/Sine or Walsh} \qquad S(u_{\vj}) = \int_{[0,1]^d} u_\vj (\vx) \, \dif \vx = \delta_{\vj,\vzero}, \qquad \cg : = \reals \\
    &\begin{array}{l}\Sapp(f,n) = \frac 1n \sum_{i=1}^n f(\vx_i) = \sum_{\vj \in \text{dual set}} \hf(\vj)  \\[4ex]
    \abs{S(f) - \Sapp(f,n)} \le \sum_{\vzero \ne \vj \in \text{dual set}} \bigabs{\hf(\vj)}
    \end{array}
    \quad \raisebox{-8ex}{\includegraphics[width=3cm]{ProgramsImages/ShiftedLatticePoints.eps} \qquad
    \includegraphics[width=3cm]{ProgramsImages/SSobolPoints.eps}}
\end{align*}

@@

@@

\begin{frame}[label = BallsWontHelp]{But I Like Balls \smallscoop!}

@@

    \item[Step 2] Choose $n$ large enough so that 
    \[
    \norm[\cg]{S(f) - \Sapp(f,n)} \le \varepsilon \qquad \forall f \in \cb_{\rho}, \qquad \text{where } \Sapp(f,n) = \sum_{i=1}^n L_i(f) g_i
    \]

    \item[Step 3] Let $\tf \in \cf$ be the \alert{minimum} norm interpolant of the data $L_1(f), \ldots, L_n(f)$.

    \item[Step 4]  If $C\bignorm[\cf]{\tf} \le \rho$ for some preset inflation factor, $C$, then return $A(f,\varepsilon) = \Sapp(f,n)$.  Otherwise, choose $\rho = 2C\bignorm[\cf]{\tf}$, and go to Step 2.
\end{description}

@@

This algorithm succeeds for the \alert{cone} \smallcone defined as those functions in $\cf$ whose norms are not much larger than their minimum norm interpolants.   \hyperlink{ConeFrame}{\beamerreturnbutton{Back}}

>>>>

\newcommand{\sol}{S}
\newcommand{\app}{A}
\newcommand{\Sapp}{S_{\textup{app}}}
\newcommand{\LambdaStd}{\Lambda^{\textup{std}}}
\newcommand{\LambdaSer}{\Lambda^{\textup{ser}}}
\newcommand{\LambdaAll}{\Lambda^{\textup{all}}}
%\DeclareMathOperator{\spann}{span}
%\DeclareMathOperator{\app}{app}

@@

    \item \hyperlink{BallsWontHelp}{\beamergotobutton{``But I really like balls!''}}
\end{itemize}

@@

\begin{frame}{Integration Using Function Values\footfullcite{DicEtal14a}}

\begin{align*}
    \cf &:= \left \{ f = \sum_{\vj \in \cn} \hf(\vj) u_{\vj} : \norm[\cf]{f} := \bignorm[1,\vlambda]{\hf} : = \norm[1]{\left(\frac{\bigabs{\hf(\vj)}}{\lambda_{\vj}} \right)_{\vj \in \cn}} \right \} \qquad \begin{minipage}{3cm}\raggedright\alert{$\vlambda$ affects convergence rate \& tractabililty}\end{minipage}\\
    u_{\vj} &= \text{Cosine/Sine or Walsh} \qquad S(u_{\vj}) = \int_{[0,1]^d} u_\vj (\vx) \, \dif \vx = \delta_{\vj,\vzero}, \qquad \cg : = \reals \\
    &\begin{array}{l}\Sapp(f,n) = \frac 1n \sum_{i=1}^n f(\vx_i)  \\[4ex]
    \abs{S(f) - \Sapp(f,n)} \le \sum_{\vzero \ne \vj \in \text{dual set}} \bigabs{\hf(\vj)}
    \end{array}
    \quad \raisebox{-8ex}{\includegraphics[width=3cm]{ProgramsImages/ShiftedLatticePoints.eps} \qquad
    \includegraphics[width=3cm]{ProgramsImages/SSobolPoints.eps}}
\end{align*}

@@

\begin{align*}
    \cf &:= \left \{ f = \sum_{\vj \in \cn} \hf(\vj) u_{\vj} : \norm[\cf]{f} := \bignorm[1,\vlambda]{\hf} : = \norm[1]{\left(\frac{\bigabs{\hf(\vj)}}{\lambda_{\vj}} \right)_{\vj \in \cn}} \right \} \qquad \begin{minipage}{3cm}\raggedright\alert{$\vlambda$ affects convergence rate \& tractabililty}\end{minipage}\\
    u_{\vj} &= \text{Cosine/Sine or Walsh} \qquad S(u_{\vj}) = \int_{[0,1]^d} u_\vj (\vx) \, \dif \vx = \delta_{\vj,\vzero}, \qquad \cg : = \reals \\
    &\begin{array}{l}\Sapp(f,n) = \frac 1n \sum_{i=1}^n f(\vx_i) = \sum_{\vj \in \text{dual set}} \hf(\vj)  \\[4ex]
    \abs{S(f) - \Sapp(f,n)} \le \sum_{\vzero \ne \vj \in \text{dual set}} \bigabs{\hf(\vj)}
    \end{array}
    \quad \raisebox{-8ex}{\includegraphics[width=3cm]{ProgramsImages/ShiftedLatticePoints.eps} \qquad
    \includegraphics[width=3cm]{ProgramsImages/SSobolPoints.eps}}
\end{align*}

@@

\section{General Problems}

@@

\begin{frame}[label = BallsWontHelp]{``But I Like Balls \smallscoop!''}

@@

    \item[Step 2] Choose $n$ large enough so that

    \vspace{-4ex}
    \begin{multline*}
     \norm[\cg]{S(f) - \Sapp(f,n)} \le \norm[\cf\to \cg]{S - \Sapp(\cdot,n)} \rho \le \varepsilon \\
         \text{where } \Sapp(f,n) = \sum_{i=1}^n L_i(f) g_i
    \end{multline*}

@@

    \item<2>[Step 3] Let $\tf \in \cf$ be the \alert{minimum} norm interpolant of the data $L_1(f), \ldots, L_n(f)$

    \item[Step 4]  \uncover<2>{If $C\bignorm[\cf]{\tf} \le \rho$ for some preset \alert{inflation} factor, $C$, }then return $A(f,\varepsilon) = \Sapp(f,n)$\uncover<2>{; otherwise, choose $\rho = 2C\bignorm[\cf]{\tf}$, and go to Step 2}
\end{description}

\uncover<2>{This succeeds for the \alert{cone} \smallcone defined as those functions in $\cf$ whose norms are not much larger than their minimum norm interpolants.   \hyperlink{ConeFrame}{\beamerreturnbutton{Back}}}
